---
title: "LEGO_v3"
author: "Xin LEI"
date: "2024-02-06"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r package}
# Install the required packages
packages <- c("ggplot2", "reshape2", "patchwork", "cowplot", "dplyr", "gbm", "caret", "Metrics")

# Check that each package is installed, and if not, install it
for(pkg in packages) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
    library(pkg, character.only = TRUE)
  }
}
```


## Specific Theme Correlation analysis

### with 9000 resale_price_new

8 continuous variables

```{r map01, fig.width=13, fig.height=9}
library(ggplot2)
library(reshape2)

# Load the data
data <- read.csv("theme_data_model.csv")

# Selecting relevant columns
selected_columns <- c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new")
correlation_data <- data[, selected_columns]

# Calculating the correlation matrix
cor_matrix <- cor(correlation_data, use = "complete.obs")

# Melting the correlation matrix for ggplot2
melted_cor_matrix <- melt(cor_matrix)

# Renaming Var1 and Var2 with custom names
melted_cor_matrix$Var1 <- factor(melted_cor_matrix$Var1,
                                 levels = c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new"),
                                 labels = c("Lifecycle Duration (Days)", "Days Since Launch (Days)", "Number of Parts", "Rating", "Retail Price (USD)", "Number of Minifigures", "Used Sets Resale Price(USD)", "New Sets Resale Price (USD)"))

melted_cor_matrix$Var2 <- factor(melted_cor_matrix$Var2,
                                 levels = c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new"),
                                 labels = c("Lifecycle Duration (Days)", "Days Since Launch (Days)", "Number of Parts", "Rating", "Retail Price (USD)", "Number of Minifigures", "Used Sets Resale Price(USD)", "New Sets Resale Price (USD)"))

# Creating the heatmap with correlation coefficients
heatmap_plot <- ggplot(melted_cor_matrix, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", value)), vjust = 1, size = 6) + 
  scale_fill_gradient(low = "white", high = "skyblue") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 18), 
    axis.text.y = element_text(size = 18), 
    plot.title = element_text(hjust = 0.5, size = 20), 
    legend.text = element_text(size = 18) , legend.title = element_text(size = 18)
    ) +
  labs(x = "", y = "", title = "Correlation Heatmap of LEGO Product Variables")

# Display heat map
print(heatmap_plot)

# Use ggsave to save the heat map
ggsave("heatmap_theme_v3_with_9000.png", plot = heatmap_plot, width = 13, height = 9, dpi = 300)
```

Put 6 correlations on a graph

```{r pic01}
library(ggplot2)
library(patchwork)
library(cowplot)

#png("Correlation_theme_v3_with_9000.png", width = 2400, height = 1600, res = 300)

# read data
data <- read.csv("theme_data_model.csv")

# lifecycle_duration and resale_price_new
cor.test_result <- cor.test(data$lifecycle_duration, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value


plot1 <- ggplot(data, aes(x = lifecycle_duration, y = resale_price_new)) +
  geom_point(color = "#F08080", alpha = 0.5) +
  geom_smooth(method = "lm", color = "black", fill = "grey", level = 0.95, alpha = 0.2) +
  labs(x = "Lifecycle Duration (Days)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value < 2.2e-16", cor.test_result$estimate), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5) +
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black"),
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# days_since_launch and resale_price_new
cor.test_result <- cor.test(data$days_since_launch, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot2 <- ggplot(data, aes(x = days_since_launch, y = resale_price_new)) +
  geom_point(color = "#FFAC1C", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Days Since Launch (Days)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value < 2.2e-16", cor.test_result$estimate), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# parts_count and resale_price_new
cor.test_result <- cor.test(data$parts_count, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot3 <- ggplot(data, aes(x = parts_count, y = resale_price_new)) +
  geom_point(color = "#FFD700", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Number of Parts", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))

# rating and resale_price_new
cor.test_result <- cor.test(data$rating, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot4 <- ggplot(data, aes(x = rating, y = resale_price_new)) +
  geom_point(color = "#008B8B", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Rating", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black"),
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# retail_price and resale_price_new
cor.test_result <- cor.test(data$retail_price, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot5 <- ggplot(data, aes(x = retail_price, y = resale_price_new)) +
  geom_point(color = "#808000", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Retail Price (USD)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# minifigures_count and resale_price_new
cor.test_result <- cor.test(data$minifigures_count, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot6 <- ggplot(data, aes(x = minifigures_count, y = resale_price_new)) +
  geom_point(color = "plum4", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Number of Minifigures", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# Combine charts using patchwork
combined_plot <- plot1 + plot2 + plot3 + plot4 + plot5 + plot6 + 
  plot_layout(ncol = 3, nrow = 2)  

# Add title
combined_plot <- combined_plot + 
  plot_annotation(
    title = "Correlation between Resale Price and Product Variables of LEGO Sets",
    theme = theme(
      plot.title = element_text(hjust = 0.5)
    )
  )

# Draw final chart
print(combined_plot)

#dev.off()
```

resale_price_new and resale_price_used

```{r fig01}
library(ggplot2)

# Read the data from CSV
data <- read.csv("theme_data_model.csv")

# Correlation analysis
cor.test_result <- cor.test(data$resale_price_new, data$resale_price_used)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

# Create the plot with points and regression line in pale yellow and grey confidence interval
plot <- ggplot(data, aes(x = resale_price_new, y = resale_price_used)) +
  geom_point(color = "#4169E1", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(title = "Correlation between Resale Prices of Used and Unopened Products", x = "Unopened Product Resale Price (USD)", y = "Used Product Resale Price (USD)") +
  annotate("text", x = 0, y = 2000, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black")+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    plot.title = element_text(hjust = 0.5),
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black")
  )

# Show the plot
print(plot)

# Save the plot as an image
ggsave("new_used_theme_v3_with_9000.png", plot, width = 10, height = 8, dpi = 300)
```

is_starwars and resale_price_new

```{r fig02_1}

# Read data
data <- read.csv("theme_data_model.csv")

# Check the data structure to make sure is_starwars is a factor type and resale_price_new is a numeric type
str(data)

# Convert is_starwars to a factor
data$is_starwars <- as.factor(data$is_starwars)

# ANOVA was used for correlation analysis
anova_result <- aov(resale_price_new ~ is_starwars, data = data)

# Displays an overview of the ANOVA results
summary(anova_result)
```

is_from_retired_theme and resale_price_new


```{r fig02_2}

# Read data
data <- read.csv("theme_data_model.csv")

# Check the data structure to ensure that is_from_retired_theme is a factor type and resale_price_new is a numeric type
str(data)

# Convert is_from_retired_theme to a factor
data$is_from_retired_theme <- as.factor(data$is_from_retired_theme)

# ANOVA was used for correlation analysis
anova_result <- aov(resale_price_new ~ is_from_retired_theme, data = data)

# Displays an overview of the ANOVA results
summary(anova_result)
```

### without 9000 resale_price_new


```{r data01}
library(dplyr)

# Read data
data <- read.csv("theme_data_model.csv")

# Filter out data whose resale_price_new value is less than 9000
filtered_data <- data %>% filter(resale_price_new < 9000)

# Save filtered data to a new file
write.csv(filtered_data, "theme_data_model_without_9000.csv", row.names = FALSE)
```


8 continuous variables

```{r map02, fig.width=13, fig.height=9}
library(ggplot2)
library(reshape2)

# Load the data
data <- read.csv("theme_data_model_without_9000.csv")

# Selecting relevant columns
selected_columns <- c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new")
correlation_data <- data[, selected_columns]

# Calculating the correlation matrix
cor_matrix <- cor(correlation_data, use = "complete.obs")

# Melting the correlation matrix for ggplot2
melted_cor_matrix <- melt(cor_matrix)

# Renaming Var1 and Var2 with custom names
melted_cor_matrix$Var1 <- factor(melted_cor_matrix$Var1,
                                 levels = c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new"),
                                 labels = c("Lifecycle Duration (Days)", "Days Since Launch (Days)", "Number of Parts", "Rating", "Retail Price (USD)", "Number of Minifigures", "Used Sets Resale Price(USD)", "New Sets Resale Price (USD)"))

melted_cor_matrix$Var2 <- factor(melted_cor_matrix$Var2,
                                 levels = c("lifecycle_duration", "days_since_launch", "parts_count", "rating", "retail_price", "minifigures_count", "resale_price_used", "resale_price_new"),
                                 labels = c("Lifecycle Duration (Days)", "Days Since Launch (Days)", "Number of Parts", "Rating", "Retail Price (USD)", "Number of Minifigures", "Used Sets Resale Price(USD)", "New Sets Resale Price (USD)"))

# Creating the heatmap with correlation coefficients
heatmap_plot <- ggplot(melted_cor_matrix, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  geom_text(aes(label = sprintf("%.2f", value)), vjust = 1, size = 6) + 
  scale_fill_gradient(low = "white", high = "skyblue") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1, size = 18), 
    axis.text.y = element_text(size = 18), 
    plot.title = element_text(hjust = 0.5, size = 20), 
    legend.text = element_text(size = 18) , legend.title = element_text(size = 18)
    ) +
  labs(x = "", y = "", title = "Correlation Heatmap of LEGO Product Variables")

# Display heat map
print(heatmap_plot)

# Use ggsave to save the heat map
ggsave("heatmap_theme_v3_without_9000.png", plot = heatmap_plot, width = 12, height = 8, dpi = 300)
```

Put 6 correlations on a graph

```{r pic02}
library(ggplot2)
library(patchwork)
library(cowplot)

#png("Correlation_theme_v3_without_9000.png", width = 2400, height = 1600, res = 300)

# Read data
data <- read.csv("theme_data_model_without_9000.csv")

# lifecycle_duration and resale_price_new
cor.test_result <- cor.test(data$lifecycle_duration, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot1 <- ggplot(data, aes(x = lifecycle_duration, y = resale_price_new)) +
  geom_point(color = "#F08080", alpha = 0.5) +
  geom_smooth(method = "lm", color = "black", fill = "grey", level = 0.95, alpha = 0.2) +
  labs(x = "Lifecycle Duration (Days)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value < 2.2e-16", cor.test_result$estimate), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black"),
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))

# days_since_launch and resale_price_new
cor.test_result <- cor.test(data$days_since_launch, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot2 <- ggplot(data, aes(x = days_since_launch, y = resale_price_new)) +
  geom_point(color = "#FFAC1C", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Days Since Launch (Days)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value < 2.2e-16", cor.test_result$estimate), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# parts_count and resale_price_new
cor.test_result <- cor.test(data$parts_count, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot3 <- ggplot(data, aes(x = parts_count, y = resale_price_new)) +
  geom_point(color = "#FFD700", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Number of Parts", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))

# rating and resale_price_new
cor.test_result <- cor.test(data$rating, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot4 <- ggplot(data, aes(x = rating, y = resale_price_new)) +
  geom_point(color = "#008B8B", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Rating", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black"),
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# retail_price and resale_price_new
cor.test_result <- cor.test(data$retail_price, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot5 <- ggplot(data, aes(x = retail_price, y = resale_price_new)) +
  geom_point(color = "#808000", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Retail Price (USD)", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# minifigures_count and resale_price_new
cor.test_result <- cor.test(data$minifigures_count, data$resale_price_new)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

plot6 <- ggplot(data, aes(x = minifigures_count, y = resale_price_new)) +
  geom_point(color = "plum4", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(x = "Number of Minifigures", y = "Resale Price (USD)") +
  annotate("text", x = 0, y = 1200, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black", size = 2.5)+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    axis.ticks.x = element_line(color = "black"),
    axis.ticks.y = element_blank(),
    axis.line.x = element_line(color = "black"),
    axis.text.y = element_blank(), 
    axis.title.y = element_blank()
  ) + scale_y_continuous(breaks = seq(0, 1200, by = 200), limits = c(0, 1200))


# Combine charts using patchwork
combined_plot <- plot1 + plot2 + plot3 + plot4 + plot5 + plot6 + 
  plot_layout(ncol = 3, nrow = 2)  

# Add title
combined_plot <- combined_plot + 
  plot_annotation(
    title = "Correlation between Resale Price and Product Variables of LEGO Sets",
    theme = theme(
      plot.title = element_text(hjust = 0.5)
    )
  )

# Draw final chart
print(combined_plot)

#dev.off()
```

resale_price_new and resale_price_used

```{r fig03}
library(ggplot2)

# Read the data from CSV
data <- read.csv("theme_data_model_without_9000.csv")

# Correlation analysis
cor.test_result <- cor.test(data$resale_price_new, data$resale_price_used)
correlation_coefficient <- cor.test_result$estimate
p_value <- cor.test_result$p.value

# Create the plot with points and regression line in pale yellow and grey confidence interval
plot <- ggplot(data, aes(x = resale_price_new, y = resale_price_used)) +
  geom_point(color = "#4169E1", alpha = 0.5) +  
  geom_smooth(method = "lm", color = "black", fill = "grey") +
  labs(title = "Correlation between Resale Prices of Used and Unopened Products", x = "Unopened Product Resale Price (USD)", y = "Used Product Resale Price (USD)") +
  annotate("text", x = 0, y = 1000, label = sprintf("R = %.2f\nP-value %s", cor.test_result$estimate, 
            ifelse(cor.test_result$p.value < .Machine$double.eps, sprintf("< %.2e", .Machine$double.eps), sprintf("= %.2f", cor.test_result$p.value))), 
            hjust = 0, vjust = 1.1, color = "black")+
  theme(
    panel.background = element_rect(fill = "white", colour = NA), 
    panel.grid = element_blank(), 
    plot.title = element_text(hjust = 0.5),
    axis.ticks = element_line(color = "black"),
    axis.line = element_line(color = "black")
  )

# Show the plot
print(plot)

# Save the plot as an image
ggsave("new_used_theme_v3_without_9000.png", plot, width = 10, height = 8, dpi = 300)
```

is_starwars and resale_price_new

```{r fig04_1}

# Read data
data <- read.csv("theme_data_model_without_9000.csv")

# Check the data structure to make sure is_starwars is a factor type and resale_price_new is a numeric type
str(data)

# Convert is_starwars to a factor
data$is_starwars <- as.factor(data$is_starwars)

# ANOVA was used for correlation analysis
anova_result <- aov(resale_price_new ~ is_starwars, data = data)

# Displays an overview of the ANOVA results
summary(anova_result)
```

is_from_retired_theme and resale_price_new


```{r fig04_2}

# Read data
data <- read.csv("theme_data_model_without_9000.csv")

# Check the data structure to ensure that is_from_retired_theme is a factor type and resale_price_new is a numeric type
str(data)

# Convert is_from_retired_theme to a factor
data$is_from_retired_theme <- as.factor(data$is_from_retired_theme)

# ANOVA was used for correlation analysis
anova_result <- aov(resale_price_new ~ is_from_retired_theme, data = data)

# Displays an overview of the ANOVA results
summary(anova_result)
```


## Price prediction model 

###GBM (data without 9000 of resale_price_new )

Remove the resale_price_used column

```{r data02}
library(dplyr)

# Read data
data <- read.csv("theme_data_model_without_9000.csv")

# Remove the 'resale_price_used' column
data <- select(data, -resale_price_used)


# Save the processed data to a new file
write.csv(data, "updated_theme_data_model_without_9000.csv", row.names = FALSE)
```

Raw data 

```{r model_v3_1, fig.width=13, fig.height=9}
library(gbm)
library(dplyr)
library(caret)
library(Metrics)

# Read data
data <- read.csv("final_model_data.csv")

# Converts categorical variables to factor types
data$is_starwars <- as.factor(data$is_starwars)
data$is_from_retired_theme <- as.factor(data$is_from_retired_theme)

# Set random seed
set.seed(123)

# Devide 80% train data and 20% test data
rows <- nrow(data)
shuffled_indices <- sample(1:rows, rows)
train_size <- floor(0.8 * rows) # Ensure it's an integer
train_indices <- shuffled_indices[1:train_size]         # 80% as train data
test_indices <- shuffled_indices[(train_size + 1):rows] # 20% as test data

train_data <- data[train_indices, ]
test_data <- data[test_indices, ]

#nrow(train_data)
#nrow(test_data)

# Parameter combination list
params <- expand.grid(n_trees = c(100, 200, 300, 400, 500),
                      interaction_depth = c(2, 3, 4),
                      shrinkage = c(0.05, 0.1, 0.15))

# Train the model and calculate the performance function
train_and_evaluate <- function(train_data, n_trees, interaction_depth, shrinkage) {
    model <- gbm(resale_price_new ~ ., data = train_data, distribution = "gaussian",
                 n.trees = n_trees, interaction.depth = interaction_depth, shrinkage = shrinkage,
                 cv.folds = 10, verbose = FALSE)
    
    predictions <- predict(model, train_data, n.trees = n_trees)
    rmse_value <- rmse(train_data$resale_price_new, predictions)
    r_square_value <- R2(train_data$resale_price_new, predictions)
    
    return(list(model = model, rmse = rmse_value, r_square = r_square_value))
}

# Iterate through parameter combinations and store the results
results <- list()
for(i in 1:nrow(params)) {
    p <- params[i, ]
    result <- train_and_evaluate(train_data, p$n_trees, p$interaction_depth, p$shrinkage)
    results[[i]] <- list(params = p, rmse = result$rmse, r_square = result$r_square)
    cat(sprintf("n_trees: %d, depth: %d, shrinkage: %.2f, RMSE: %.2f, R2: %.2f\n",
                p$n_trees, p$interaction_depth, p$shrinkage, result$rmse, result$r_square))
}

# Find the best results
best_rmse <- Inf
best_params <- NULL
best_r_square <- -Inf

for(result in results) {
    if(result$rmse < best_rmse) {
        best_rmse <- result$rmse
        best_params <- result$params
        best_r_square <- result$r_square
    }
}

# Displays the best combination of parameters and their performance
cat("Best Parameters:\n")
print(best_params)
cat(sprintf("Best RMSE: %.2f\n", best_rmse))
cat(sprintf("Best R-square: %.2f\n", best_r_square))

# Evaluate the model on the test data set, using the best parameters found
best_n_trees <- best_params$n_trees
best_interaction_depth <- best_params$interaction_depth
best_shrinkage <- best_params$shrinkage

best_model <- train_and_evaluate(train_data, best_n_trees, best_interaction_depth, best_shrinkage)$model
predictions_test <- predict(best_model, test_data, n.trees = best_n_trees)
rmse_test <- rmse(test_data$resale_price_new, predictions_test)
r_square_test <- R2(test_data$resale_price_new, predictions_test)
Correlation_test <- cor(test_data$resale_price_new, predictions_test)


cat("RMSE on Test Set:", rmse_test, "\n")
cat("R-square on Test Set:", r_square_test, "\n")
cat("Correlation on Test Set:", Correlation_test, "\n")


# Make predictions
predictions_all <- predict(best_model, data, n.trees = best_n_trees)

# Visual prediction results
library(ggplot2)
# Create chart
plot <- ggplot(data, aes(x = resale_price_new, y = predictions_all)) +
  geom_point(shape = 3, size = 2, color = "#008B8B") +
  geom_abline(slope = 1, intercept = 0, color = 'black', linetype = "dashed") + 
  labs(x = "Actual Price (USD)", y = "Predicted Price (USD)", title = "Actual Price vs Predicted Price\n(Gradient Boosting Machine Model on Original Data）") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 26, hjust = 0.5),
    axis.title = element_text(size =24, color = 'black'),
    axis.text = element_text(size = 24, color = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks = element_line(linewidth = 1),
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
    axis.line = element_line(colour = "black", linewidth = 0.5))

#show the plot
plot

# Save the picture as a PNG file
ggsave("GBM_raw_v3.png", plot, width = 13, height = 9, dpi = 300)
```

Logarithm of data

```{r data03}
library(dplyr)

# Read data
data <- read.csv("updated_theme_data_model_without_9000.csv")

# Applying the log conversion to the specified column, minifigures_count adds 1 to take the logarithm
data_transformed <- data %>%
  mutate(across(.cols = -c(is_starwars, is_from_retired_theme, rating, minifigures_count),
                .fns = ~ log(.))) %>%
  mutate(minifigures_count = log(minifigures_count + 1))

# Save the processed data to a new file
write.csv(data_transformed, "log_transformed_model_data_theme.csv", row.names = FALSE)
```


```{r model_v3_2, fig.width=13, fig.height=9}
library(gbm)
library(dplyr)
library(caret)
library(Metrics)

# Read data
data <- read.csv("final_model_data_log.csv")

# Converts categorical variables to factor types
data$is_starwars <- as.factor(data$is_starwars)
data$is_from_retired_theme <- as.factor(data$is_from_retired_theme)

# Set random seed
set.seed(123)

# Devide 80% train data and 20% test data
rows <- nrow(data)
shuffled_indices <- sample(1:rows, rows)
train_size <- floor(0.8 * rows) # Ensure it's an integer
train_indices <- shuffled_indices[1:train_size]         # 80% as train data
test_indices <- shuffled_indices[(train_size + 1):rows] # 20% as test data

train_data <- data[train_indices, ]
test_data <- data[test_indices, ]

#nrow(train_data)
#nrow(test_data)

# Parameter combination list
params <- expand.grid(n_trees = c(100, 200, 300, 400, 500),
                      interaction_depth = c(2, 3, 4),
                      shrinkage = c(0.05, 0.1, 0.15))

# Train the model and calculate the performance function
train_and_evaluate <- function(train_data, n_trees, interaction_depth, shrinkage) {
    model <- gbm(resale_price_new ~ ., data = train_data, distribution = "gaussian",
                 n.trees = n_trees, interaction.depth = interaction_depth, shrinkage = shrinkage,
                 cv.folds = 10, verbose = FALSE)
    
    predictions <- exp(predict(model, train_data, n.trees = n_trees))
    rmse_value <- rmse(exp(train_data$resale_price_new), predictions)
    r_square_value <- R2(exp(train_data$resale_price_new), predictions)
    
    return(list(model = model, rmse = rmse_value, r_square = r_square_value))
}

# Iterate through parameter combinations and store the results
results <- list()
for(i in 1:nrow(params)) {
    p <- params[i, ]
    result <- train_and_evaluate(train_data, p$n_trees, p$interaction_depth, p$shrinkage)
    results[[i]] <- list(params = p, rmse = result$rmse, r_square = result$r_square)
    cat(sprintf("n_trees: %d, depth: %d, shrinkage: %.2f, RMSE: %.2f, R2: %.2f\n",
                p$n_trees, p$interaction_depth, p$shrinkage, result$rmse, result$r_square))
}

# Find the best results
best_rmse <- Inf
best_params <- NULL
best_r_square <- -Inf

for(result in results) {
    if(result$rmse < best_rmse) {
        best_rmse <- result$rmse
        best_params <- result$params
        best_r_square <- result$r_square
    }
}

# Displays the best combination of parameters and their performance
cat("Best Parameters:\n")
print(best_params)
cat(sprintf("Best RMSE: %.2f\n", best_rmse))
cat(sprintf("Best R-square: %.2f\n", best_r_square))

# Evaluate the model on the test data set, using the best parameters found
best_n_trees <- best_params$n_trees
best_interaction_depth <- best_params$interaction_depth
best_shrinkage <- best_params$shrinkage

best_model <- train_and_evaluate(train_data, best_n_trees, best_interaction_depth, best_shrinkage)$model
predictions_test <- exp(predict(best_model, test_data, n.trees = best_n_trees))
rmse_test <- rmse(exp(test_data$resale_price_new), predictions_test)
r_square_test <- R2(exp(test_data$resale_price_new), predictions_test)
Correlation_test <- cor(test_data$resale_price_new, predictions_test)

cat("RMSE on Test Set:", rmse_test, "\n")
cat("R-square on Test Set:", r_square_test, "\n")
cat("Correlation on Test Set:", Correlation_test, "\n")

# Make predictions
predictions_all_transformed <- exp(predict(best_model, data, n.trees = best_n_trees))


# Visual prediction results
library(ggplot2)
# Create chart
plot <- ggplot(data, aes(x = exp(resale_price_new), y = predictions_all_transformed)) +
  geom_point(shape = 3, size = 2, color = "#008B8B") +
  geom_abline(slope = 1, intercept = 0, color = 'black', linetype = "dashed") +  
  labs(x = "Actual Price (USD)", y = "Predicted Price (USD)", title = "Actual Price vs Predicted Price\n(Gradient Boosting Machine Model on Logarithmic Data）") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 26, hjust = 0.5),
    axis.title = element_text(size =24, color = 'black'),
    axis.text = element_text(size = 24, color = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.ticks = element_line(linewidth = 1),
    panel.border = element_rect(colour = "black", fill = NA, linewidth = 1),
    axis.line = element_line(colour = "black", linewidth = 0.5))

#show the plot
plot

# Save the picture as a PNG file
ggsave("GBM_log_v3.png", plot, width = 13, height = 9, dpi = 300)
```

