---
title: "Unlocking the Pattern: A Remarkable Plunge in Youth Crime Rates in New Zealand from 2015 to 2022"
author: "Thanh Tra Ngo"
output: pdf_document
date: "2023-09-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


```{r, message=FALSE, warning=FALSE, include=FALSE}
# Load data
rawdata <- read.csv("Ethnicity_AES_v1.csv", stringsAsFactors = FALSE)

# Load library
library(ggplot2)
library(tidyverse)
library(dplyr)
library(stringr)
library(ggpubr)
library(knitr)
library(kableExtra)
library(rmarkdown)

# Data pre-processing
# Change year.month to Year
rawdata$Year <- unclass(substring(rawdata$Year.Month, first = 4, last = 7))
rawdata$Year <- as.numeric(as.character(rawdata$Year))

# change colname sex = gender
colnames(rawdata)[colnames(rawdata) == 'SEX'] <- 'Gender'

# Create another AgeGroup includes only 4 age groups: 0-14, 15-24, 25-34, over 35
rawdata1 <- rawdata %>% 
  mutate(AgeGroup = case_when(str_detect(Age.Group, "0-4|5-9|10-14" ) ~ "0-14",
                              str_detect(Age.Group, "15-19|20-24" ) ~ "15-24",
                              str_detect(Age.Group, "25-29|30-34" ) ~ "25-34",
                              TRUE ~ "35+"))

# Drop unnecessary variables
data <- rawdata1[, !names(rawdata1) %in% c("Person.Organisation", "Year.Month", "ANZSOC.Subdivision", "Method.of.Proceeding", "Age.Group")]
```

```{r include=FALSE}
# Subset data of youth offenders
youth <- subset(rawdata, Age.Group %in% c("15-19", "20-24"), !names(rawdata) %in% c("Person.Organisation", "Year.Month", "ANZSOC.Subdivision", "Method.of.Proceeding"))
```

# 1. Introduction
In New Zealand (NZ), individuals aged 15 to 24 involving to crimes, referred to youth offenders, accounted for nearly 40% of all offenders in 2015 (Table 1). From 2015 to 2022, young people and emerging adults represented an average of 33.8% of all apprehensions in the country (Table A2.2a). This report aims to provide comprehensive insights into the profile of New Zealand's youth offenders during the period spanning 2015 to 2022, shedding light on their offending patterns. Offending data from New Zealand Police is used to ascertain whether New Zealand's youth offending rate experienced any changes during this time frame, and if so, whether these changes varied by ethnicity, gender, or the types of crimes committed. This report will focus on the two key questions. First, what trends can be observed in New Zealand's youth offender numbers compared to the overall offender population from 2015 to 2022, based on legal proceedings? Second, what is the profile of New Zealand's youth offending engage in gender distribution, ethnic composition and crime behavior? The subsequent sections of this report will delve into the data collection, the methodology, and the detailed results for each of the aforementioned questions.

# 2. Methods
## 2.1	Dataset
The raw data related to the ethnicity and age groups of offenders in New Zealand was sourced from policedata.nz, specifically under the "Proceedings (Offenders Demographics)" category and the "Demographics" tab. Access to this information is available on the New Zealand Police website. The dataset covers an 8-year period, spanning from 2015 to 2022. 

To facilitate analysis, data pre-processing was conducted, resulting in the retention of only the essential variables, forming a dataset comprising 350,131 observations across 7 key variables. These variables include Ethnic group, Age group, Gender, ANZSOC.Division, ANZSOC.Group, Proceedings and Year. Furthermore, a specific subset of the dataset was extracted, focusing on offenders aged 15 to 24 years old, commonly referred to as youth offenders. This subset retains the same 7 variables and consists of 100,168 observations. For a comprehensive understanding of the dataset, data summary is provided in Table A1.1 and Table A1.2 and detailed variable definition is shown in Table A1.3 in Appendix 1. Descriptive statistics for all the variables can be found in Appendix 2.

## 2.2 Method

In this study, the descriptive methodology is mainly employed, utilizing statistical calculations such as minimum, maximum, mode, median, and mean, as well as graphical representations including line graphs, bar graphs, and tables. The dataset featured several variables categorized as follows: $Ethnic.Group$, $Age.Group$, $Gender$, $ANZSOC.Division$ and $ANZSOC.Group$ which all were classified as nominal variables. Meanwhile, $Year$ and $Proceedings$ were categorized as discrete numeric variables. For data analysis, R programming language is utilized for data cleaning, data summary and data visualization through the application of R packages such as ggplot2, dplyr, tidyr, tidyverse, stringr, ggpubr. 

# 3. Results
## 3.1 What trends can be observed in New Zealand's youth offenders compared to the overall offender population from 2015 to 2022, based on legal proceedings?
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 12, fig.align = "center"}
data_year <- data %>% 
  group_by(Year) %>% 
  summarise(Proceedings = sum(Proceedings, na.rm = TRUE))

youth_year <- youth %>% 
  group_by(Year) %>% 
  summarise(Youth_offenders = sum(Proceedings, na.rm = TRUE))

plot1 <- ggplot() +
  geom_line(data = data_year, aes(x=Year, y=Proceedings), color = 'blue') + 
  geom_line(data = youth_year, aes(x=Year, y=Youth_offenders), color = '#A2CD5A') +
  ggtitle("Figure 1. NZ's total offenders vs. youth offenders (2015-2022)")

plot1
```

Figure 1 illustrates a noticeable parallel in trends between youth offending and overall offender population in New Zealand. For the progression of general crimes in New Zealand, in 2015, there were 154,536 reported proceedings, which increased to 171,724 cases in 2016. Subsequently, these numbers exhibited a gradual decline over the following years, dropping by 31.9% to reach at 117,014 proceedings in 2022 (Detailed numbers in Table A2.5a, Appendix 2). Focusing on youth offenders, their pattern is equally noteworthy. In 2015, there were 61,537 youth offender proceedings, which escalated to 66,149 cases in 2016. However, the ensuing years witnessed a dramatic decrease in youth offending, culminating in a notable 49.2% reduction, with only 33,611 proceedings recorded in 2022 (Detailed numbers in Table A2.5b, Appendix 2).

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 12, fig.height=4, fig.align = "center"}
data_age <- data %>% 
  group_by(Year, AgeGroup) %>% 
  summarise(Proceedings = sum(Proceedings, na.rm = TRUE))

plot2 <- ggplot(data_age, aes(x=Year, y=Proceedings, group = AgeGroup)) +
  geom_line(aes(color=AgeGroup)) +
  ggtitle("Figure 2. NZ's offenders by age group from 2015 to 2022")

plot2
```

Figure 2, presented herein, reveals a compelling trend when comparing youth offenders to other age groups of 0-14, 25-34, and individuals over 35. This analysis underscores a substantial decline in youth offending since the year 2016. As corroborated by Table 1 as below, in the year 2015, youth offenders constituted nearly 40% of the total offender population in New Zealand, establishing themselves as the preeminent demographic engaged in criminal activities. This prominence persisted for the subsequent three years and over the spanning from 2015 to 2022, youth crime consistently accounted for the highest proportion of 33.8% of total offender population (Table A2.2a, Appendix 2). However, a shift in this pattern became evident after 2019. Presently, the highest proportion of offenders falls within the 25-34 age group, while youth offenders have transitioned to become the second-largest offender group as of 2022, comprising 28.72% of the total offender population. 

### Table 1. The proportion (%) of NZ's youth offenders in overall offender population (2015 - 2022)
```{r echo=FALSE, message=FALSE, warning=FALSE}
data_group <- data %>% group_by(Year, AgeGroup) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings))

tab1 <- xtabs(Number_of_Proceedings ~ AgeGroup + Year, data_group) 

tab1 <- round(100 * prop.table(tab1,2), 2)

tab1 = tab1[order(tab1[,"2015"], decreasing = TRUE),]

kable(tab1) %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

## 3.2. What is the profile of New Zealand's youth offending engage in age group, gender distribution, ethnic composition and crime behavior?
### The profile of NZ's youth offending by age group and gender distribution.
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 10, fig.height=3, fig.align = "center"}
plot3 <- 
  youth %>%
  group_by(Year, Age.Group) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Year, y=Proceedings, fill=Age.Group)) +
  geom_bar(stat="identity", position="fill")+
  scale_fill_manual(values=c("#CFF2ED", "#46849B"))+
  labs(title="Figure 3. NZ's youth offdeners by Age group (2015-2022)",
       x="Year",
       y="Proceedings")+
  theme(axis.text.x=element_text(angle=60, hjust=1),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))
plot3
```

Overall, an examination of Figure 3 reveals that there is a relatively equal distribution between the two age groups, 15-19 and 20-24, within the category of youth offenders. Over the time span from 2015 to 2022, the 20-24 age group consistently represents a substantial portion, precisely 53.66% of youth offenders, as indicated in Table A2.2b within Appendix 2.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 12, fig.height=4, fig.align = "center"}
plot4 <- 
  youth %>%
  group_by(Year, Gender) %>%
  filter(Gender != "Not Stated") %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Year, y=Proceedings, fill=Gender)) +
  geom_bar(stat="identity", position="dodge")+
  geom_text(aes(label=format(Proceedings,big.mark=",")),
            position = position_dodge(width = 0.9), 
            vjust = -0.5)+
  scale_fill_manual(values=c("#CFF2ED", "#46849B"))+
  labs(title="Figure 4. NZ's youth offdeners by Gender (2015-2022)",
       x="Year",
       y="Procedings")+
  theme(axis.text.x=element_text(angle=60, hjust=1),
        plot.title = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12),
        legend.title = element_text(size=12),
        legend.text = element_text(size=12),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))
plot4
```

Regarding gender dynamics, Figure 4 portrays that the majority of youth offenders are male, accounting for 77.41% of youth offenders throughout the period spanning from 2015 to 2022. This gender distribution is marginally higher when compared to the composition within the broader population of offenders, where the proportion of males stands at 76.17%. (Table A2.3a and Table A2.3b, Appendix 2).

### The profile of NZ's youth offending by ethnic composition and the relationship between ethnicity and age group. 
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.height=7, fig.align = "center", fig.width = 18}
plot5 <- 
  youth %>%
  group_by(Year, Ethnic.Group) %>%
  filter(Ethnic.Group != "Not Stated") %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Year, y=Proceedings, fill=Ethnic.Group)) +
  geom_bar(stat="identity", position="fill")+
  scale_fill_manual(values=c("#F0A693", "#46849B", "#9CC3D3", "#BFEFFF",
                             "#8EE1D6", "#8FBC8F"))+
  labs(title="Figure 5. NZ's youth offenders by ethnic group (2015-2022)",  
              y="Percentage")+
theme(axis.text.x=element_text(angle=60,
                                 hjust=1),
        legend.position = "bottom",
        legend.title = element_text(size=10),
        legend.text = element_text(size=10),
        plot.title = element_text(size=10),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))

plot6 <- youth %>%
  group_by(Ethnic.Group, Age.Group) %>%
  filter(Ethnic.Group != "Not Stated") %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Proceedings, y=Ethnic.Group, fill=Age.Group)) +
  geom_bar(stat="identity", position="fill")+
  scale_fill_manual(values =c("#CFF2ED", "#46849B")) +
  labs(title="Figure 6. The relationship between age group and ethnicity of NZ's youth offenders",
       x="Percentage",
       y="Ethnicity",
       fill = "Age Group")+
  theme(axis.text.x=element_text(angle=60,
                                 hjust=1),
        legend.position = "bottom",
        legend.title = element_text(size=10),
        legend.text = element_text(size=10),
        plot.title = element_text(size=10),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=10),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))
 
ggarrange(plot5, plot6, nrow = 1, legend="bottom")

```

As depicted in Figure 5, Māori, European, and Pacific Island youth offenders consistently constituted a significant majority in crime activities from 2015 to 2022. The combined representation of there main ethnicities comprises 87.03% of youth offenders and 89.06% of all offenders in New Zealand (refer to Table A2.1a and Table A2.1b in Appendix 2). Among these groups, Māori youth offenders accounted for a substantial proportion, starting at 43.99% in 2015 and maintaining stability throughout the specified period. Meanwhile, European youth offenders, initially representing 37.46% in 2015, declined to 24.06% of New Zealand's youth offenders by 2022. Pacific Island youth offenders constituted the third-largest group, with a representation of 10.48% in 2015, which decreased to 8.83% in 2022. Detailed year-by-year ethnic composition of youth offenders can be found in Table A3.1 within Appendix 3.

Figure 6 provides a compelling insight, revealing that over 60% of Asian offenders aged 20-24 and approximately 75% of Indian offenders aged 20-24 are associated with youth offending activities, while other ethnic groups exhibit a more balanced distribution across young age groups.

### What are the prevalent crime types associated with New Zealand's youth offenders?

Data presented in Table A2.4b in Appendix 2 shows an overview of youth offending crime types in New Zealand from 2015 to 2022. Notably, the most prevalent crime type in both the youth offending and overall offender population is "Traffic and Vehicle Regulatory Offences", which represents nearly 19% of New Zealand's youth offending during this period.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 16, fig.height=6, fig.align = "center"}

top_5_crime_type <-
  youth %>%
  group_by(ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  arrange(desc(Proceedings)) %>%
  head(5)

youth %>%
  group_by(ANZSOC.Division, Year) %>%
  filter(ANZSOC.Division %in% top_5_crime_type$ANZSOC.Division) %>%
  summarise("Total_Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Year,
             y=Total_Proceedings,
             colour=reorder(ANZSOC.Division, desc(Total_Proceedings))))+
  geom_line(size=1)+
  geom_point(size=2)+
  labs(title="Figure 7. Top five crime types in NZ's youth offending between 2015 and 2022",
       x="Year",
       y="Proceedings",
       fill="ANZSOC.Division")+
  theme(axis.text.x=element_text(angle=60,hjust=1),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))+
  scale_color_manual(values = c("#2BA191","#EF7A1A","#8FBC8F" ,"#E9C46A", "#264653"), name=NULL)

```

Figure 7 can be observed that top five crime types experienced increases from 2015 to 2016, except for "Theft and Related Offences". "Theft and Related Offences" exhibited a decline starting from 2015, showing an decrease of nearly 60% in proceedings from 2015 to 2022. Since 2016, all categories witnessed reduction in their respective proceedings, except for "Traffic and Vehicle Regulatory Offences", which saw a 10.5% increase after 2021, from 6,768 cases in 2021 to 7,478 cases in 2022. Among these groups, "Public Order Offences" has the most substantial decline, dropping by 73.8% since 2016, from 7,924 cases in 2016 to 2,073 cases in 2022. "Dangerous of Negligent Acts Endangering Persons", meanwhile, showed a modest increase of 1.3% since 2021, from 5,046 cases in 2021 to 5,114 cases in 2022. Detailed data on crime types of youth offenders based on proceedings can be found in Table A3.2 within Appendix 3.

#### The relationship between crime types and age group 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 16, fig.height=5, fig.align = "center"}
plot8 <- youth %>%
  group_by(ANZSOC.Division, Age.Group) %>%
  filter(ANZSOC.Division %in% top_5_crime_type$ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Proceedings, y=ANZSOC.Division, fill=Age.Group)) +
  geom_bar(stat="identity", position="fill")+
  scale_fill_manual(values =c("#CFF2ED", "#46849B")) +
  labs(title="Figure 8.  Age group distribution among NZ's youth offenders within each top 5 crime type",
       x="Percentage",
       y="Crime type",
       fill = "Age Group")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))
  
plot8

```

Based on the information presented in Figure 8 and Table A3.3 in Appendix 3, over 61% of the age group 15-19 is associated with "Theft and Related Offences" which includes activities like the illegal use of a motor vehicle, theft from retail premises. Meanwhile, for the group 20-24, over 65% of the offenses are related to "Traffic and Vehicle Regulatory Offences", such as driving without a licence, driving while licence disqualified or suspendedand, exceeding the prescribed content of alcohol or other substance limit. Additionally, "Offences Against Justice Procedures, Govt Sec and Govt Ops", such as breach of bail, also accounts for a substantial portion of 67.5% of group 20-24. Further details about the specific crime types can be found in Table A3.4 in Appendix 3. 

#### The relationship between crime types and ethnicity.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 16, fig.height=5, fig.align = "center"}
plot9 <- youth %>%
  group_by(Ethnic.Group, ANZSOC.Division) %>%
  filter(Ethnic.Group != "Not Stated") %>%
  filter(ANZSOC.Division %in% top_5_crime_type$ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  ggplot(aes(x=Proceedings, y=ANZSOC.Division, fill=Ethnic.Group)) +
  geom_bar(stat="identity", position="fill")+
  scale_fill_manual(values=c("#F0A693", "#46849B", "#9CC3D3", "#BFEFFF",
                             "#8EE1D6", "#8FBC8F", "#E9C46A"))+
  labs(title="Figure 9. Ethnic distribution within each type of youth crime",
       x="Percentage",
       y="Crime type",
       fill = "Ethnic Group")+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "grey"))
plot9
```
  
Figure 9 provides a breakdown of the ethnicity proportions within each type of youth crime. Notably, four out of the top five crime types, including "Theft and Related Offences", "Offences Against Justice Procedures, Government Security, and Government Operations", "Acts Intended to Cause Injury, and "Traffic and Vehicle Regulatory Offences" exhibit the highest association with Māori youth offenders. The exception to this pattern is "Dangerous or Negligent Acts Endangering Persons", which has the highest linkage to European youth offenders.

The table A3.5 in Appendix 3 shows another aspect which illustrates the proportion of crime types within each youth offending ethnicity. For Māori youth offenders, the predominant crime activities include "Traffic and Vehicle Regulatory Offences" (25.8%), "Theft and Related Offences" (24.33%), and "Acts Intended to Cause Injury" (22.57%). In contrast, European youth offenders are primarily involved in "Traffic and Vehicle Regulatory Offences" (31.34%), "Acts Intended to Cause Injury" (20.23%) and "Dangerous or Negligent Acts Endangering Persons" (20.05%). Pacific Island youth offenders exhibit a slightly different pattern, with their most common crime activities being "Traffic and Vehicle Regulatory Offences" (32.2%), "Acts Intended to Cause Injury" (22.81%), and "Offences Against Justice Procedures, Government Security, and Government Operations" (17.08%).

# 4. Discussion

This study examined trends in New Zealand’s youth offending between 2015 and 2022 and confirmed the sharp decline in the number of youth offenders since 2016. The majority of youth offenders are male, constituting for 77.41% of youth offenders throughout over the period. Notably, Māori, European, and Pacific Island youth offenders consistently represented a significant portion of those involved in criminal activities, accounting for 87.03% of all youth offenders in the country. Among these ethnic groups, Māori youth offenders remained relatively stable throughout the specified period, whereas European and Pacific Island youth offenders exhibited declines in their numbers. It is suggested that the root causes of youth offending may be more deeply initiated from young people's families, whānau, and communities than solely individual factors. Consequently, it emphasizes the importance of government agencies finding effective engagement methods and providing support to communities to prevent youth offending and re-offending.

\newpage
# Appendix
## Appendix 1
### Table A1.1: Summary data for New Zealand's general offenders from 2015 to 2022, based on proceedings
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(head(rbind(summary(data)))) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position", font_size = 8)
```

### Table A1.2: Summary data of New Zealand' youth offenders from 2015 to 2022, based on proceedings
```{r echo=FALSE, message=FALSE, warning=FALSE}
kable(head(rbind(summary(youth)))) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position", font_size = 8) 
```
### Table A1.3: Variable definitions in the dataset
```{r echo=FALSE, message=FALSE, warning=FALSE}
Variable_Name <- c("Ethnic.Group", "AgeGroup", "Gender", "ANZSOC.Division", "ANZSOC.Group", "Proceedings", "Year")
Definition <- c("The ethnicity of offenders", "The age group of offenders","The gender of offenders", "The crime type of offenders", "Details in crime type of offenders", "The number of proceedings", "The time recorded for offenders (in Year)")
Variable_Type <- c("Categorical", "Categorical", "Categorical", "Categorical", "Categorical", "Numerical", "Numerical")
Level_of_Measurement <- c("Nominal", "Nominal", "Nominal", "Nominal", "Nominal", "Discrete", "Discrete")

df_var <- data.frame(Variable_Name, Definition, Variable_Type, Level_of_Measurement)

kable(rbind(df_var), align = "llcc") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

## Appendix 2: Descriptive statistics of variables in the dataset
### Table A2.1a Frequency table of Ethnic group in NZ's general crimes"

```{r echo=FALSE, message=FALSE, warning=FALSE}
a21a <- data %>% group_by(Ethnic.Group) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Number_of_Proceedings/ sum(Number_of_Proceedings))*100,2),"%")) %>% 
  arrange(desc(Number_of_Proceedings))

kable(head(a21a), align = "lrr") %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.1b Frequency table of Ethnic group in NZ's youth crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a21b <- youth %>% group_by(Ethnic.Group) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Number_of_Proceedings/ sum(Number_of_Proceedings))*100,2),"%")) %>% 
  arrange(desc(Number_of_Proceedings))

kable(head(a21b), align = "lrr") %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")

```

### Table A2.2a Frequency table of Age group in NZ's general crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a22a <- data %>% group_by(AgeGroup) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Number_of_Proceedings/ sum(Number_of_Proceedings))*100,2),"%")) 

kable(head(a22a), align = "ccc") %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.2b Frequency table of Age group in NZ's youth crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a22b <- youth %>% group_by(Age.Group) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Number_of_Proceedings/ sum(Number_of_Proceedings))*100,2),"%")) %>% 
  arrange(desc(Percentage))

kable(head(a22b), align = "ccc") %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.3a Frequency table of Gender in NZ's general crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a23a <- data %>% group_by(Gender) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>% 
  arrange(desc(Percentage))

kable(a23a, align = "lrr") %>%
   kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.3b Frequency table of Gender in NZ's youth crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a23b <- youth %>% group_by(Gender) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>% 
  arrange(desc(Percentage))

kable(a23b, align = "lcc") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.4a Frequency table of ANZSOC.Division (Crime type) in NZ's general crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a24a <- data %>% group_by(ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>% 
  arrange(desc(Proceedings))

kable(a24a, align = "lrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")

```

### Table A2.4b Frequency table of ANZSOC.Division (Crime type) in NZ's youth crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a24b <- youth %>% group_by(ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>%
  arrange(desc(Proceedings))

kable(a24b, align = "lrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A2.5a Frequency table of ANZSOC.Group (Detailed in crime type) in NZ's general crimes (Just show top 10 ANZSOC.Group with highest percentages)
```{r echo=FALSE, message=FALSE, warning=FALSE}
a25a <- data %>% group_by(ANZSOC.Group) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>% 
  arrange(desc(Proceedings)) %>%
  head(10)

kable(a25a, align = "lrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")

```

### Table A2.5b Frequency table of ANZSOC.Group (Detailed in crime type) in NZ's youth crimes (Just show top 10 ANZSOC.Group with highest percentages)
```{r echo=FALSE, message=FALSE, warning=FALSE}
a25b <- youth %>% group_by(ANZSOC.Group) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) %>%
  arrange(desc(Proceedings)) %>%
  head(10)

kable(a25b, align = "lrr") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")


```

### Table A2.6a Frequency table of Year in NZ's general crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a26a <- data %>% group_by(Year) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) 

kable(a26a, align = "ccc") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```
### Table A2.6b Frequency table of Year in NZ's youth crimes
```{r echo=FALSE, message=FALSE, warning=FALSE}
a26b <- youth %>% group_by(Year) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  mutate("Percentage" = paste0(round((Proceedings/ sum(Proceedings))*100,2),"%")) 

kable(a26b, align = "ccc") %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

## Appendix 3 
### Table A3.1 Ethnic composition (in percent) among NZ's youth offenders from 2015 to 2022
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14}
youth_group <- youth %>% group_by(Year, Ethnic.Group) %>%
  summarise("Number_of_Proceedings" = sum(Proceedings))
  
a31 <- xtabs(Number_of_Proceedings ~ Ethnic.Group + Year, youth_group) 

a31 <- round(100 * prop.table(a31,2), 2)

a31 = a31[order(a31[,"2015"], decreasing = TRUE),]

kable(head(a31)) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")
```

### Table A3.2 Top ten crime types of NZ's youth offenders from 2015 to 2022, based on proceedings
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14}
Crime_type <-
  youth %>%
  group_by(Year, ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings))
  
a32 <- xtabs(Proceedings ~ ANZSOC.Division + Year, Crime_type)
a32 = a32[order(a32[,"2015"], decreasing = TRUE),] %>%
  head(10)

kable(head(a32)) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position", font_size = 8)
```
### Table A3.3 The crime types among youth offending by age groups
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14}
a33 <- youth %>%
  group_by(Age.Group, ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  arrange(desc(Proceedings))

a33 <- xtabs(Proceedings ~ ANZSOC.Division + Age.Group, a33)

a33 <- round(100 * prop.table(a33,1), 2)

kable(a33) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position")

```
### Table A3.4 Top 20 crime types in details among youth offending, based on proceedings
```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14}
a34 <- youth %>% 
  group_by(Age.Group, ANZSOC.Division, ANZSOC.Group) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  arrange(desc(Proceedings)) %>%
  head(20)

kable(a34) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position", font_size = 4)

```
### Table A3.5 The proportion of crime types (%) within each youth offending ethnicity

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.width = 14}
a35 <- youth %>%
  group_by(Ethnic.Group, ANZSOC.Division) %>%
  filter(Ethnic.Group != "Not Stated") %>%
  filter(ANZSOC.Division %in% top_5_crime_type$ANZSOC.Division) %>%
  summarise("Proceedings" = sum(Proceedings)) %>%
  arrange(desc(Proceedings))

a35 <- xtabs(Proceedings ~ ANZSOC.Division + Ethnic.Group, a35)

a35 <- round(100 * prop.table(a35,2), 2)

kable(a35) %>%
  kable_styling(full_width = FALSE, bootstrap_options = "striped", latex_options = "HOLD_position", font_size = 8)

```